Manuscript Figures

### 2018-07-08 Manuscript Figures.Rmd
Updates to graph

```{r chromosome_plot_exp, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=8, fig.height=6}
subgenome.positions <-
  subgenome %>%
  left_join(B73.v4.gene.positions, by=c("gene2"="geneID")) %>%
  select(Chromosome, Pos_start, Pos_end, subgenome) %>%
  rename(Subgenome=subgenome) %>%
  subset(Subgenome %in% c("sub1", "sub2"))

@@

df1 <- B73.v4.centromere.positions
df1$x <- -.45
df1$xend <- .45
df2 <- subgenome.positions
df2$x <- -.45
df2$xend <- -.05
df3 <- dominant_homeolog_exp
df3$x <- .05
df3$xend <- .45
segment_data <- bind_rows(df2,df3)
segment_data <- segment_data[!is.na(segment_data$Pos_start),]
segment_data <-
  segment_data %>%
  ungroup()
segment_data$Subgenome[segment_data$Subgenome %in% c("sub1")] <- "Maize1"
segment_data$Subgenome[segment_data$Subgenome %in% c("sub2")] <- "Maize2"
# segment_data$Subgenome[segment_data$Subgenome %in% c("dom")] <- "Dominant Homeolog"
segment_data <- segment_data %>% subset(Subgenome %in% c("Maize1", "Maize2", "Dominant Expression"))
centromere_data <- df1

## Make the plot
chromosome_plot_exp <-
  ggplot(data=B73.v4.chr.size) +
  geom_bar(aes(B73.v4.chr.size$chromosome, B73.v4.chr.size$size), stat="identity", fill="grey70") +
  # geom_segment(data=segment_data, aes(x=Chromosome+x, xend=Chromosome+xend, y=Pos_start, yend=Pos_end, colour=Subgenome), size=.001) +
  geom_rect(data=segment_data, inherit.aes = F, aes(xmin=Chromosome+x, xmax=Chromosome+xend, ymin=Pos_start, ymax=Pos_end, color=Subgenome, fill=Subgenome)) +
  geom_rect(data=centromere_data, inherit.aes = F, aes(xmin=Chromosome+x, xmax=Chromosome+xend, ymin=Pos_start, ymax=Pos_end)) +
  scale_fill_manual(values=c("green", "red", "blue", "black")) +
  scale_color_manual(values=c("green", "red", "blue", "black")) +
  scale_x_discrete(limits=c("Chr1","Chr2","Chr3","Chr4","Chr5","Chr6","Chr7","Chr8","Chr9","Chr10")) +
  scale_y_continuous(labels=format_si())
chromosome_plot_exp  +
  labs(
    # title="Subgenome Locations by Chromosome",
    x="Chromosome",
    y="Position on Chromosome"
  )
```

<!-- # ```{r chromosome_plot_abundance, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=8, fig.height=6} -->
<!-- # subgenome.positions <- -->
<!-- #   subgenome %>% -->
<!-- #   left_join(B73.v4.gene.positions, by=c("gene2"="geneID")) %>% -->
<!-- #   select(Chromosome, Pos_start, Pos_end, subgenome) %>% -->
<!-- #   rename(Subgenome=subgenome) %>% -->
<!-- #   subset(Subgenome %in% c("sub1", "sub2")) -->
<!-- #  -->
<!-- # dominant_homeolog_abun <- expressedProteinsPairs -->
<!-- # dominant_homeolog_abun$Subgenome <- "no dominance" -->
<!-- # dominant_homeolog_abun$Subgenome[dominant_homeolog_abun$dNSAF_mean1 / dominant_homeolog_abun$dNSAF_mean2 > 2] <- "Dominant Abundance" -->
<!-- # dominant_homeolog_abun$Subgenome[dominant_homeolog_abun$dNSAF_mean2 / dominant_homeolog_abun$dNSAF_mean1 > 2] <- "Dominant Abundance" -->
<!-- # dominant_homeolog_abun$Maize1[dominant_homeolog_abun$dNSAF_mean2 / dominant_homeolog_abun$dNSAF_mean1 > 2] <- dominant_homeolog_abun$Maize2[dominant_homeolog_abun$dNSAF_mean2 / dominant_homeolog_abun$dNSAF_mean1 > 2] -->
<!-- # df0 <- dominant_homeolog_abun[dominant_homeolog_abun$Subgenome %in% c("no dominance"),] -->
<!-- # df0$Maize1 <- df0$Maize2 -->
<!-- # dominant_homeolog_abun <- bind_rows(dominant_homeolog_abun, df0) -->
<!-- # dominant_homeolog_abun <- -->
<!-- #   dominant_homeolog_abun %>% -->
<!-- #   select(Maize1, Subgenome) %>% -->
<!-- #   left_join(B73.v4.gene.positions, by=c("Maize1"="geneID")) %>% -->
<!-- #   select(Chromosome, Pos_start, Pos_end, Subgenome) -->
<!-- #  -->
<!-- # df1 <- B73.v4.centromere.positions -->
<!-- # df1$x <- -.45 -->
<!-- # df1$xend <- .45 -->
<!-- # df2 <- subgenome.positions -->
<!-- # df2$x <- -.45 -->
<!-- # df2$xend <- -.05 -->
<!-- # df3 <- dominant_homeolog_abun -->
<!-- # df3$x <- .05 -->
<!-- # df3$xend <- .45 -->
<!-- # segment_data <- bind_rows(df2,df3) -->
<!-- # segment_data <- segment_data[!is.na(segment_data$Pos_start),] -->
<!-- # segment_data <- -->
<!-- #   segment_data %>% -->
<!-- #   ungroup() -->
<!-- # segment_data$Subgenome[segment_data$Subgenome %in% c("sub1")] <- "Maize1" -->
<!-- # segment_data$Subgenome[segment_data$Subgenome %in% c("sub2")] <- "Maize2" -->
<!-- # # segment_data$Subgenome[segment_data$Subgenome %in% c("dom")] <- "Dominant Homeolog" -->
<!-- # segment_data <- segment_data %>% subset(Subgenome %in% c("Maize1", "Maize2", "Dominant Abundance")) -->
<!-- # centromere_data <- df1 -->
<!-- #  -->
<!-- # ## Make the plot -->
<!-- # chromosome_plot_abundance <- -->
<!-- #   ggplot(data=B73.v4.chr.size) + -->
<!-- #   geom_bar(aes(B73.v4.chr.size$chromosome, B73.v4.chr.size$size), stat="identity", fill="grey70") + -->
<!-- #   # geom_segment(data=segment_data, aes(x=Chromosome+x, xend=Chromosome+xend, y=Pos_start, yend=Pos_end, colour=Subgenome), size=.001) + -->
<!-- #   geom_rect(data=segment_data, inherit.aes = F, aes(xmin=Chromosome+x, xmax=Chromosome+xend, ymin=Pos_start, ymax=Pos_end, color=Subgenome, fill=Subgenome)) + -->
<!-- #   geom_rect(data=centromere_data, inherit.aes = F, aes(xmin=Chromosome+x, xmax=Chromosome+xend, ymin=Pos_start, ymax=Pos_end)) + -->
<!-- #   scale_fill_manual(values=c("green", "red", "blue", "black")) + -->
<!-- #   scale_color_manual(values=c("green", "red", "blue", "black")) + -->
<!-- #   scale_x_discrete(limits=c("Chr1","Chr2","Chr3","Chr4","Chr5","Chr6","Chr7","Chr8","Chr9","Chr10")) + -->
<!-- #   scale_y_continuous(labels=format_si()) -->
<!-- # chromosome_plot_abundance  + -->
<!-- #   labs( -->
<!-- #     # title="Subgenome Locations by Chromosome", -->
<!-- #     x="Chromosome", -->
<!-- #     y="Position on Chromosome" -->
<!-- #   ) -->
<!-- # ``` -->

@@

```{r GOTerms_by_subgenome, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4, fig.height=4}
#EXP only, MF terms only
grid.newpage()
GOTerms_by_subgenome_a <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct() %>% nrow(),
  area2 = goAnnotations.sub2 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct() %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct(),  
                         goAnnotations.sub2 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct()
                         ) %>% nrow(), 
  category = c("Maize1", "Maize2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=GOTerms_by_subgenome_a), top="GO Term by Subgenome\n(EV-EXP, MF only)")

@@

#EXP only, MF only
grid.newpage()
GOTerms_by_subgenome_b <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% nrow(),
  area2 = converted %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(gene2, goTerm) %>% distinct(), 
                         converted %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(gene2, goTerm) %>% distinct()
                         ) %>% nrow(), 
  category = c("Maize1", "Maize2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=GOTerms_by_subgenome_b), top="GO Term Assignments by Subgenome\n(EV-EXP, MF only)")

>>>>

```{r chromosome_plot_exp, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=10, fig.height=5}
subgenome.positions <-
  subgenome %>%
  left_join(B73.v4.gene.positions, by=c("gene2"="geneID")) %>%
  select(Chromosome, Pos_start, Pos_end, subgenome) %>%
  rename(Subgenome=subgenome) %>%
  subset(Subgenome %in% c("sub1", "sub2"))

@@

df1 <- B73.v4.centromere.positions
df1$x <- -.5
df1$xend <- .05
df2 <- subgenome.positions
df2$x <- -.45
df2$xend <- -.05
df3 <- dominant_homeolog_exp
df3$x <- .05
df3$xend <- .25
segment_data <- bind_rows(df2,df3)
segment_data <- segment_data[!is.na(segment_data$Pos_start),]
segment_data <-
  segment_data %>%
  ungroup()
segment_data$Subgenome[segment_data$Subgenome %in% c("sub1")] <- "Maize1"
segment_data$Subgenome[segment_data$Subgenome %in% c("sub2")] <- "Maize2"
# segment_data$Subgenome[segment_data$Subgenome %in% c("dom")] <- "Dominant Homeolog"
segment_data <- segment_data %>% subset(Subgenome %in% c("Maize1", "Maize2", "Dominant Expression"))
centromere_data <- df1

## Make the plot
chromosome_plot_exp <-
  ggplot(data=B73.v4.chr.size) +
  geom_bar(aes(B73.v4.chr.size$chromosome, B73.v4.chr.size$size), stat="identity", fill="grey70") +
  # geom_segment(data=segment_data, aes(x=Chromosome+x, xend=Chromosome+xend, y=Pos_start, yend=Pos_end, colour=Subgenome), size=.001) +
  geom_rect(data=segment_data, inherit.aes = F, aes(xmin=Chromosome+x, xmax=Chromosome+xend, ymin=Pos_start, ymax=Pos_end, color=Subgenome, fill=Subgenome)) +
  geom_rect(data=centromere_data, inherit.aes = F, aes(xmin=Chromosome+x, xmax=Chromosome+xend, ymin=Pos_start, ymax=Pos_end)) +
  scale_fill_manual(values=c("green", "red", "blue", "black")) +
  scale_color_manual(values=c("green", "red", "blue", "black")) +
  scale_x_discrete(limits=c("Chr1","Chr2","Chr3","Chr4","Chr5","Chr6","Chr7","Chr8","Chr9","Chr10")) +
  scale_y_continuous(labels=format_si())
chromosome_plot_exp  +
  labs(
    # title="Subgenome Locations by Chromosome",
    x="Chromosome",
    y="Position on Chromosome"
  ) + coord_flip()
```

@@

```{r GOTerms_by_subgenome, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=4, fig.height=4}
# #EXP only, MF terms only
# grid.newpage()
# GOTerms_by_subgenome_a <- draw.pairwise.venn(
#   area1 = goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct() %>% nrow(),
#   area2 = goAnnotations.sub2 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct() %>% nrow(),
#   cross.area = intersect(goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct(),  
#                          goAnnotations.sub2 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct()
#                          ) %>% nrow(), 
#   category = c("Maize1", "Maize2"), 
#   lty = rep("blank", 2), 
#   fill = c("light blue", "green"), 
#   alpha = rep(0.5, 2), 
#   cat.pos = c(0, 180), 
#   scaled = FALSE,
#   euler.d = FALSE, 
#   sep.dist = 0.3, 
#   rotation.degree = 0,
#   ind = FALSE
# )
# grid.arrange(gTree(children=GOTerms_by_subgenome_a), top="GO Term by Subgenome\n(EV-EXP, MF only)")
# 
# ## Only keep genes where there is a duplicate still on subgenome 1 and subgenome 2.  The converted data.frame will hold maize2 genes with the names replaced with maize1 homologs
# converted <-
#   homeologs.pairs %>%
#   subset(Maize1 != "" & Maize2 != "") %>%
#   right_join(., goAnnotations.sub2,by=c("Maize2"="gene2"))
# converted$Maize2[!is.na(converted$Maize1)] <- as.character(converted$Maize1[!is.na(converted$Maize1)])
# converted <- 
#   converted %>%
#   select(Maize2, goTerm, evCode, type) %>%
#   rename(gene2=Maize2)
# 
# #EXP only, MF only
# grid.newpage()
# GOTerms_by_subgenome_b <- draw.pairwise.venn(
#   area1 = goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% nrow(),
#   area2 = converted %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% nrow(),
#   cross.area = intersect(goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(gene2, goTerm) %>% distinct(), 
#                          converted %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(gene2, goTerm) %>% distinct()
#                          ) %>% nrow(), 
#   category = c("Maize1", "Maize2"), 
#   lty = rep("blank", 2), 
#   fill = c("light blue", "green"), 
#   alpha = rep(0.5, 2), 
#   cat.pos = c(0, 180), 
#   scaled = FALSE,
#   euler.d = FALSE, 
#   sep.dist = 0.3, 
#   rotation.degree = 0,
#   ind = FALSE
# )
# grid.arrange(gTree(children=GOTerms_by_subgenome_b), top="GO Term Assignments by Subgenome\n(EV-EXP, MF only)")

#EXP only, MF terms only
grid.newpage()
GOTerms_by_subgenome_a <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct() %>% nrow(),
  area2 = goAnnotations.sub2 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct() %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct(),  
                         goAnnotations.sub2 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(goTerm) %>% distinct()
                         ) %>% nrow(), 
  category = c("Maize1", "Maize2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=GOTerms_by_subgenome_a), top="GO Term by Subgenome\n(EV-EXP, MF only)")

@@

#EXP only, MF only
grid.newpage()
GOTerms_by_subgenome_b <- draw.pairwise.venn(
  area1 = goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% nrow(),
  area2 = converted %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% nrow(),
  cross.area = intersect(goAnnotations.sub1 %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(gene2, goTerm) %>% distinct(), 
                         converted %>% filter(evCode=="EXP") %>% filter(type=="MF") %>% select(gene2, goTerm) %>% distinct()
                         ) %>% nrow(), 
  category = c("Maize1", "Maize2"), 
  lty = rep("blank", 2), 
  fill = c("light blue", "green"), 
  alpha = rep(0.5, 2), 
  cat.pos = c(0, 180), 
  scaled = FALSE,
  euler.d = FALSE, 
  sep.dist = 0.3, 
  rotation.degree = 0,
  ind = FALSE
)
grid.arrange(gTree(children=GOTerms_by_subgenome_b), top="GO Term Assignments by Subgenome\n(EV-EXP, MF only)")
```
